Distributed Version Control Systems

### 2010-05-18 paper.tex
Agregadas algunas imagenes
Se agrego el apartado del repositorio centralizado

\newcommand{\latexiie}{\LaTeX2{\Large$_\varepsilon$}}
\usepackage{graphicx}
%\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
%\usepackage{ieeetc}	% if you want the "trans. comp." style
%\usepackage{ieeeimtc}	% if you want the IMTC conference style

@@

@@

\subsection{Centralized repository with integration manager}
It is possible to have a single central repository where all developers have read access. Everyone has an official public version from which they can work from. Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed. When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
It is also possible to have an automatic integration manager. This server will accept pushes, run all tests and if everything is ok it will then push this changes to the central repository. Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).

>>>>

\newcommand{\latexiie}{\LaTeX2{\Large$_\varepsilon$}}
\usepackage{graphicx}

\newcommand{\diagrama}[1]{\begin{center}
    \includegraphics[width=.8\linewidth, keepaspectratio]{#1} 
\end{center}}

%\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
%\usepackage{ieeetc}	% if you want the "trans. comp." style
%\usepackage{ieeeimtc}	% if you want the IMTC conference style

@@

\diagrama{PeerCodeReview.jpg}

\subsection{Centralized server}
The classic workflow where there is one central server which has the whole project is also available. In this case all developers has access to the server and can pull and push changes from it. The main advantages is that any developer can share changes among other developer without needing to use the central server. However once a piece of code is considered finished it should be pushed to this server.

\diagrama{RepoCentral.jpg}

@@

\diagrama{IndependentSubteams.jpg}
\subsection{Centralized repository with integration manager}
It is possible to have a single central repository where all developers have read access. Everyone has an official public version from which they can work from. Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed. When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
It is also possible to have an automatic integration manager. This server will accept pushes, run all tests and if everything is ok it will then push this changes to the central repository. Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).

\diagrama{ResponsableIntegracion.jpg}
